Poster Data Analysis

### 2018-09-06 notebooks/poster_analysis.Rmd
added poster title

# Description
This notebook presents the analysis of whole genome data for the poster "", presented at the ASM NGS Conference in Washington D.C. September 2018.

>>>>

# Description
This notebook presents the analysis of whole genome data for the poster "Quinolone resistance mechanisms found in E. coli from four animal species in Norway
", presented at the ASM NGS Conference in Washington D.C. September 2018.
